---
title: "Facs analysis"
author: Alexis Hucteau
date: "`r Sys.Date()`"
output:
    html_document:
      toc: yes
      toc_float: yes
      theme: united
editor_options:
  markdown:
    wrap: sentence
---

Back to [PhD Project](https://alexishucteau.github.io/PhD_project/)

```{r, include=F}
library(ggplot2)

Diff_facs_analysis <- read.csv("Data/Diff_AGI.csv")
Rhod2_facs_analysis <- read.csv("Data/Rhod2_AGI.csv")
PpIX_facs_analysis <- read.csv("Data/PpIX_AGI_ALA_Basal.csv")
Scenith_analysis <- read.csv("Data/Scenith.csv")
```

# Summary

* [Rhod2](#rhod2)
* [PpIX](#ppix)
* [PPIX flux](#ppix-flux)
* [Scenith](#scenith)
  * [Glycolyse dependency](#glycolyse)
  * [Mitochondria dependency](#mito)
* [Differenciation](#diff)
  * [CD11b](#cd11b)
  * [CD14](#cd14)
  * [CD15](#cd15)

# Rhod2, calcium indicator {#rhod2}

```{r}
ggplot(data=Rhod2_facs_analysis, aes(x = Cell.line, y = Rhod2, color = factor(Treatment, levels = c("DMSO", "AGI")))) +
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Calcium indicator", x = "Cell lines")+
  theme_minimal()
```

# PpIX {#ppix}

```{r}
ggplot(data=PpIX_facs_analysis, aes(x = Cell.line, y = MFI_PpIX, color = factor(Treatment, levels = c("DMSO", "AGI")))) + 
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "PpIX indicator", x = "Cell lines")+
  theme_minimal()
```

# PpIX flux (ALA/basal) {#ppix-flux}

```{r}
ggplot(data=PpIX_facs_analysis, aes(x = Cell.line, y = ALA.basal, color = factor(Treatment, levels = c("DMSO", "AGI")))) + 
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "PpIX ALA/basal", x = "Cell lines")+
  theme_minimal()
```

# Scenith {#scenith}

PDF files:

* [M14 + DMSO](https://alexishucteau.github.io/PhD_project/Analysis/Wetlab/Data/Scenith_M14R132_DMSO.pdf)
* [M14 + AGI](https://alexishucteau.github.io/PhD_project/Analysis/Wetlab/Data/Scenith_M14R132_AGI.pdf)

## Glycolyse dependency {#glycolyse}

```{r}
ggplot(data=Scenith_analysis, aes(x=factor(Treatment, levels = c("DMSO", "AGI")), y=Gly_dependency, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Glycolyse dependency", x = "Treatment")+
  theme_minimal()
```

## Mitochondria dependency {#mito}

```{r}
ggplot(data=Scenith_analysis, aes(x=factor(Treatment, levels = c("DMSO", "AGI")), y=Mito_dependency, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Mitochondria dependency", x = "Treatment")+
  theme_minimal()
```

# Differenciation markers {#diff}

## CD11b {#cd11b}

```{r}
ggplot(data=Diff_facs_analysis[c(1:4),], aes(x=Cell.line, y=CD11b_PE_A, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD11b", x = "Cell lines")+
  theme_minimal()
```

## CD14 {#cd14}

```{r}
ggplot(data=Diff_facs_analysis[c(1:4),], aes(x=Cell.line, y=CD14.APC__A700_A, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD14", x = "Cell lines")+
  theme_minimal()
```

## CD15 {#cd15}

```{r}
ggplot(data=Diff_facs_analysis[c(1:4),], aes(x=Cell.line, y=CD15_APC_A, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD15", x = "Cell lines")+
  theme_minimal()
```

